% Created 2018-06-21 Thu 20:26
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\author{Nicholas Yang}
\date{\today}
\title{GraphQL Framework}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.2.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
\tableofcontents


\section{Idea}
\label{sec-1}
A framework based around GraphQL that takes the ease of use of Rails
and strips out all the crud. Allows for fast, easy to build APIs

\section{Key Features}
\label{sec-2}
\begin{itemize}
\item Easy GraphQL Object Type definition (integrated with classes ideally)
\item Automated queries:
\end{itemize}

\begin{verbatim}
class Article < GraphQL::Object
  query_on :title  # 9Makes the query article_by_title
end
\end{verbatim}

\begin{itemize}
\item Well integrated ORM for automatic field resolving:
\end{itemize}

\begin{verbatim}
class Article < GraphQL::Object

  # Fields
  field :title, types.String
  field :title, types[Comment]

  # Queries
  query_on :title

  # Associations
  belongs_to :section
  has_many :comments # Could be optional, since fields already specifies this
end

class Comment < GraphQL::Object  
  # Fields
  field :content, types.String

end
\end{verbatim}

Should allow for:

\begin{verbatim}
article_by_title {
  title
  comments {
    content
  }
}
\end{verbatim}

\begin{itemize}
\item GraphQL by default, no REST (not that REST is bad, just that GraphQL always feels tacked on)

\item Super nice code generation. Able to introspect and see what generators have been applied (migrations for generators?)

\item Decent JWT support

\item Authorization levels

\item Instead of Model-View-Controller, how about Model-Resolver-Query? Or Model-Resolver-Query-Mutation?
\end{itemize}

\section{Design Questions}
\label{sec-3}

\begin{itemize}
\item What language? Ruby is probably easiest, but least popular.
\begin{itemize}
\item Could start in one language then port over to others like JS
\item Try Crystal? Elixir?
\end{itemize}

\item What name? Lattice? Ruby on Lattice?

\item How should middleware work?

\item How can we get authorization and authentication to work smoothly?

\item How can we improve error handling from GraphQL-Ruby?
\end{itemize}
% Emacs 25.2.1 (Org mode 8.2.10)
\end{document}